---
title: "Mandarin"
output: word_document
---

This is the same as the permCantonese file, but has some additional mixed models analysis for comparing with the permutation test.

```{r}
## permutation script 2019
require(ggplot2)
require(lme4)
require(stringr)
require(nlme)         ## for lme()
require(lsmeans)      ## for lsmeans()
# may need to run this command if the following doesn work install.packages("multcomp")
require(multcomp)  ## for multiple comparison stuff
require(remef)
#Set your working directory
#  Go to Session in menu, go to Set Working Directory, 
#  click on To Source File Location
print(sessionInfo())

apaformat <- function(p){
     p = p + theme_bw() # make the theme black-and-white rather than grey (do this before font changes, or it overrides them)
     p = p + theme(
#          plot.title = theme_text(face="bold", size=14), # use theme_get() to see available options
#          axis.title.x = theme_text(face="bold", size=12),
#          axis.title.y = theme_text(face="bold", size=12, angle=90),
          panel.grid.major = element_blank(), # switch off major gridlines
          panel.grid.minor = element_blank(), # switch off minor gridlines
#          legend.position = c(0.2,0.8), # manually position the legend (numbers being from 0,0 at bottom left of whole plot to 1,1 at top right)
#          legend.title = theme_blank(), # switch off the legend title
#          legend.text = theme_text(size=12),
#          legend.key.size = unit(1.5, "lines"),
          legend.key = element_blank() # switch off the rectangle around symbols in the legend
     )
     return(p)
}

# data frame with onset for each region
onsetStimCL = data.frame(SentenceType=c(rep("Subject",4),rep("Object",5)),cat = c("VN","DE","DCL","Head","N","V","DE","DCL","Head"), onset=c(0,0.808,1.02,1.49,0,0.431,0.767,1.027,1.427))
onsetStimCL$HeadNoun = "DCL"
onsetStimDE = data.frame(SentenceType=c(rep("Subject",3),rep("Object",4)),cat = c("VN","DE","Head","N","V","DE","Head"), onset=c(0,0.797,0.972,0,0.493,0.821,0.963))
onsetStimDE$HeadNoun = "DE"
onsetStim = rbind(onsetStimCL,onsetStimDE)
onsetStim$time = onsetStim$onset * 1000
#onsetStim$time2=c(onsetStim$time[2:length(onsetStim$time)],0)
#onsetStim$time2[onsetStim$cat=="Head"] = 1000*c(2.001,1.876,1.479,1.501)
onsetStim$time2 = c(805,1017,1487,2001, #subject DCL offsets
                    428,764,1024,1424,1876, # object DCL
                    794,969,1479, # subject DE
                    490, 818,960,1501) # object DE
onsetStim$ypos = 0.95
onsetStim$ypos[onsetStim$SentenceType == "Object"] = 0.75
onsetStim$target = 1
onsetStim$restarg = 0
onsetStim[onsetStim$cat=="Head",]

aggregate(time2 ~ HeadNoun + cat, onsetStim, mean)

bothdataAll=read.csv("ManRC eyetracking data-4yrs-final.csv")
bothdata=bothdataAll
xtabs(~ Participant,bothdata)
bothdata$HeadNoun <- factor(bothdata$HeadNoun,labels=c("DCL","DE"))
bothdata$SentenceType=factor(bothdata$SentenceType,labels=c("Subject","Object"))

bothdata$Item = str_replace(bothdata$Item,"(S|O)","I")
bothdata$time = as.numeric(as.character(bothdata$time))
bothdata$time = bothdata$time * 1000
bothdata$target = bothdata$T
#/(both$T+both$D)
xtabs(~ Participant + HeadNoun , bothdata)
xtabs(~ Participant + SentenceType , bothdata)
xtabs(~ Item + HeadNoun , bothdata)
xtabs(~ Item + SentenceType, bothdata)


means.df = aggregate(cbind(target) ~ time + HeadNoun + SentenceType, bothdata, mean)
p = ggplot(means.df , aes( x = time, y = target, colour=SentenceType))
p = p + geom_line()
p = p + scale_colour_brewer(palette="Set1")
p = p + theme_bw()   # change background to white
p = p + ylab("Target Proportions")
#p = p + ylim(0,1)
p = p + facet_wrap(~ HeadNoun, ncol=1)
p = p + geom_rect(data=onsetStim,aes(xmin=time,xmax = time2-33, ymin=ypos-0.13, ymax=ypos,colour=SentenceType),fill=NA, show.legend=FALSE)
p = p + geom_text(data=onsetStim,aes(x=(time+time2)/2, y=ypos-0.05, label=cat),hjust=0.7,size=3,show.legend=FALSE)
p
```

Above is the raw data, below we remove the mean of time 0.

```{r}
meansubset = subset(bothdata,time == 0)
meanpartitemdf = aggregate(target ~  Participant + Item + HeadNoun + SentenceType, meansubset, mean)
both = merge(bothdata,meanpartitemdf, all.x=TRUE,by=c("Participant","Item","HeadNoun","SentenceType"),sort=F)
both$target = both$target.x-both$target.y
# plot figure for dataset
means.df = aggregate(cbind(target) ~ time + HeadNoun + SentenceType, both, mean)
p = ggplot(means.df , aes( x = time, y = target, colour=SentenceType))
p = p + geom_line()
p = p + scale_colour_brewer(palette="Set1")
p = p + theme_bw()   # change background to white
p = p + ylab("Looks to target")
#p = p + ylim(0,1)
p = p + facet_wrap(~ HeadNoun, ncol=1)
p = p + geom_rect(data=onsetStim,aes(xmin=time,xmax = time2-33, ymin=ypos-0.13, ymax=ypos,colour=SentenceType),fill=NA, show.legend=FALSE)
p = p + geom_text(data=onsetStim,aes(x=(time+time2)/2, y=ypos-0.05, label=cat),size=3,show.legend=FALSE)
p
#ggsave("new.png")
```

Here is a mixed model analysis using 200 ms windows

```{r}
winsize = 200

#unique(both$time)
both$win = as.integer((both$time+10)/winsize) # like floor
xtabs(~ win, both)
both = subset(both, win != 12 & !is.na(time)) # not enough data in 12
xtabs(~ win, both)
xtabs(~ Item  + SentenceType+ win, both)
xtabs(~ Participant + SentenceType, both)

subjmeans.df = aggregate(target ~ win + HeadNoun + SentenceType + Participant + Item, both, mean)
subjmeans.df$time=subjmeans.df$win*winsize
subjmeans.df$cwin = subjmeans.df$win - mean(subjmeans.df$win)
subjmeans.df$cCL = ifelse(subjmeans.df$HeadNoun == "DCL",0.5,-0.5)
subjmeans.df$cobject = ifelse(subjmeans.df$SentenceType == "Object",0.5,-0.5)
subjmeans.df$Participant=factor(subjmeans.df$Participant)
subjmeans.df$Item=factor(subjmeans.df$Item)
mixmodel = lmer(target ~ cwin*cCL*cobject + (1 + cCL + cobject| Participant) + (1 | Item), subjmeans.df)
summixed=summary(mixmodel)
print(summixed)

mixmodel2 = update(mixmodel, . ~ . - cwin:cCL:cobject)
anova(mixmodel,mixmodel2)

```

Since we have a significant three way interaction of HeadNoun, SentenceType, and window, we can do posthocs.
We use lsmeans to do contrasts between obj and sub for each window in each HeadNoun.
lsmeans also adjusts p automatically for the number of comparisons.
This is the "right" analysis if you wanted to use a traditional mix model.  But it assumes
that each window is independent and that is not right. 
Permutation test yields similar results without these incorrect assumptions.

```{r}
options(contrasts = c("contr.treatment", "contr.poly"))
# may need to run this command if the following doesn work install.packages("nlme")
subjmeans.df$win = factor(subjmeans.df$win)
subjmeans.df$HeadNoun = factor(subjmeans.df$HeadNoun)
subjmeans.df$SentenceType = factor(subjmeans.df$SentenceType)
mixmodelFactor = lmer(target ~ win*HeadNoun*SentenceType + (1 + HeadNoun+SentenceType| Participant) + (1+SentenceType | Item), subjmeans.df)
#print(summary(mixmodelFactor))
#save(mixmodelFactor,"mixmodelSentSlopeFactor.RData")

model.lsmobj <- lsmeans(mixmodelFactor, ~  SentenceType | HeadNoun* win)
posthocs = summary(as.glht(pairs(model.lsmobj)))
print(posthocs)


subjmeans.df$pred <- remef(mixmodelFactor, ran = "all")
means2.df = aggregate(cbind(pred,target) ~ time + HeadNoun + SentenceType, subjmeans.df, mean)
timelist = as.integer(unique(subjmeans.df$time))
p = ggplot(means2.df , aes( x = time, y = target, colour=SentenceType))
meanwin= data.frame(time= rep(timelist,2),HeadNoun=rep(c("DCL","DE"),each=length(timelist)))
#meanwin$time = (meanwin$win-1)*winsize
meanwin$pval = as.numeric(lapply(posthocs, function(x){ return( x$test$pvalues[1]) }) )
meanwin$target = 0
meanwin$pred =0
meanwin$SentenceType = "Object"
meansigPost = subset(meanwin,pval < 0.05) 
# color them grey
p = p + geom_rect(data=meansigPost,aes(xmin=time, xmax=time+winsize, ymin = 0, ymax= 1.0),fill="grey90",show.legend=FALSE)
p = p + geom_line()
p = p + facet_wrap(~ HeadNoun, ncol=1)
p = p + scale_colour_brewer(palette="Set1")
p = p + scale_fill_brewer(palette="Set2")
p = p + geom_vline(xintercept = seq(0,2400,by=winsize),colour="black", linetype = 2)
#apaformat(p)
```

This is the permutation analysis

```{r}
# create copy of data frame
pdata = both[!is.na(both$time),]
wdivsize = 1
pdata$cobject = ifelse(pdata$SentenceType == "Subject",0.5,-0.5)
pdata$cDErc = ifelse(pdata$HeadNoun == "DE",0.5,-0.5)
pdata$win = as.integer(pdata$time/wdivsize)
#xtabs(~ win, pdata)
pdata$time = pdata$win*wdivsize

#pdata$target = pdata$restarg
# create data frame which averages over subjects.  
# This also stores the results of the permutation analysis
means.df = aggregate(target ~ SentenceType + cobject + time + HeadNoun, pdata, mean)
means.df$pstr = 1000

# We do this for each 100 ms window in the data
timelist = unique(pdata$time)
for (t in timelist){
    # create data frame for ONE timebin for each HeadNounuage
    onetime = subset(pdata,time == t)
    
    # do regression model on target using structure SentenceTypeition
    onemodel = summary(lm(target ~ cobject*cDErc, onetime))
    # print(summary(onemodel))
    coefonemodel = coef(onemodel)
    # this is the t-value for structure
    objT = coefonemodel[2,3]  # observed t-value
    objP = abs(coefonemodel[2,4])  # observed p-value
    means.df$objT[means.df$time == t] = objT
    means.df$objP[means.df$time == t] = objP
    deT = coefonemodel[3,3]  # observed t-value
    deP = abs(coefonemodel[3,4])  # observed p-value
    means.df$deT[means.df$time == t] = deT
    means.df$deP[means.df$time == t] = deP
    intT = coefonemodel[4,3]  # observed t-value
    intP = abs(coefonemodel[4,4])  # observed p-value
    means.df$intT[means.df$time == t] = intT
    means.df$intP[means.df$time == t] = intP
    
      randDCL = subset(onetime, HeadNoun=="DCL")
      onemodelDCL = summary(lm(target ~ cobject, randDCL))
      coefonemodelDCL = coef(onemodelDCL)
      dclstrT = coefonemodelDCL[2,3]  # observed t-value
      randDE = subset(onetime, HeadNoun=="DE")
      onemodelDE = summary(lm(target ~ cobject, randDE))
      coefonemodelDE = coef(onemodelDE)
      destrT = coefonemodelDE[2,3]  # observed t-value
    means.df$dclstrT[means.df$time == t] = dclstrT
    means.df$destrT[means.df$time == t] = destrT
}
# to see these p-values, we draw them arbitrarily on the graph at 0.2.
# when the p-value < 0.05, we draw a blue line above 0.2
# when the p-value > 0.05, we draw an orange line below 0.2
pliney = -0.1
plinemax = 0.2
means.df$plineobjP = pliney+plinemax*(0.05-means.df$objP)
means.df$plinecolobjP = ifelse(means.df$objP < 0.05,"a","b")
plineydeP = -0.3
means.df$plinedeP = plineydeP+plinemax*(0.05-means.df$deP)
means.df$plinecoldeP = ifelse(means.df$deP < 0.05,"a","b")
plineyInt = -0.5
means.df$plineintP = plineyInt+plinemax*(0.05-means.df$intP)
means.df$plinecolintP = ifelse(means.df$intP < 0.05,"a","b")


wsize = mean(pdata$time[2:5] - pdata$time[1:4] - 8)/2
means.df$SentenceType=factor(means.df$SentenceType,levels=c("Subject","Object"))
p = ggplot(means.df , aes( x = time, y = target, colour=SentenceType))
p = p + facet_wrap(~ HeadNoun, ncol=1)
p = p + geom_line()
p = p + scale_colour_brewer(palette="Set1")
p = p + scale_fill_brewer(palette="Set2")
p = p + theme_bw()   # change background to white
p = p + geom_rect(aes(xmin=time-wsize, xmax=time+wsize, ymin = pliney, ymax= plineobjP, fill=plinecolobjP),colour=NA,show.legend=FALSE)
p = p + geom_rect(aes(xmin=time-wsize, xmax=time+wsize, ymin = plineydeP, ymax= plinedeP, fill=plinecoldeP),colour=NA,show.legend=FALSE)
p = p + geom_rect(aes(xmin=time-wsize, xmax=time+wsize, ymin = plineyInt, ymax= plineintP, fill=plinecolintP),colour=NA,show.legend=FALSE)
p
```

```{r}
# Also, each window is not independent, so we create clusters for adjacent windows with p<0.05
# cnum is the cluster number and we increment the number when the p value is > 0.05
# so clusters with the same cnum are part of the same cluster
cnum = 1
lastpval = 100
lasttdir = 1
means.df$cnum = 1
for (t in timelist[2:length(timelist)]){
    onetime = subset(means.df,time == t & HeadNoun == "DCL" & SentenceType == "Object")
    pval = abs(onetime$intP)
    tdir = onetime$intT
    if (pval < 0.05 & lastpval > 0.05 ){
      cnum = cnum + 1  # increase cluster number when entering a significant cluster from a non-significant cluster
    }
    if (pval > 0.05 ){  
      cnum = cnum + 1 # increase cluster number when not significant
    }else{
      # if t value flips direction, even if both are signif, 
      # we should treat those as separate clusters
      if (lasttdir*tdir < 0){
        cnum = cnum + 1 
      }
    }
    lastpval = pval
    lasttdir = tdir
    means.df$cnum[means.df$time == t] = cnum
}
head(means.df,10)

plineyInt=-0.1
means.df$plineintP = plineyInt+plinemax*(0.05-means.df$intP)
# this shows the clusters
p = ggplot(means.df , aes( x = time, y = target, colour=SentenceType, label=cnum))
p = p + scale_colour_brewer(palette="Set1")
p = p + scale_fill_brewer(palette="Set2")
p = p + theme_bw()   # change background to white
p = p + ylab("Looks to passive match")
#p = p + ylim(0,1)
p = p + facet_wrap(~ HeadNoun, ncol=1)
p = p + geom_rect(aes(xmin=time-wsize, xmax=time+wsize, ymin = plineyInt, ymax= plineintP, fill=plinecolintP),colour=NA,show.legend=FALSE)
p + geom_text(size=2)
```


```{r}
# we now want to identify the clusters that were significant
# p-values are same for active and passive, so we just used the active items.
meansonlyact.df = subset(means.df, HeadNoun == "DCL" & SentenceType == "Object")
sigcluster = subset(meansonlyact.df, abs(intP) < 0.05 )
print(sigcluster,digits=3)
# this computes the sum of the t-values for each cluster
sumcluster  = aggregate(cbind(intT,dclstrT,destrT) ~ cnum + HeadNoun, meansonlyact.df, sum)
head(sumcluster)

# here are the start and finish bits
timedf = aggregate(time ~ cnum + HeadNoun,sigcluster,min)
colnames(timedf)<-c("cnum","HeadNoun","starttime")
timedf2 = aggregate(time ~ cnum + HeadNoun,sigcluster,max)
timedf$endtime = timedf2$time+33
print(timedf)
paste(timedf$starttime,"-",timedf$endtime,"ms",sep="",collapse=",")
```


```{r}
# now we create a distribution of t-values (save in permdist)
# by randomly scrambling the active and passive labels for each time window 1000 times
createPermDist <- function(filename="permDist.RData"){
  n = 1000
  exptests = data.frame()
  for (s in 1:length(sigcluster$time)){
    #  print(cl)
    cl = sigcluster$cnum[s] # cluster number
    b = sigcluster$time[s] # time
    print(paste("b ",b))
    # one time point
    onetime = subset(pdata, time %in% b)
    # randSet is a copy of onetime that is scrambled
    randSet = onetime
    
    for (i in 1:n){
      #  set.seed(i)
      # randomly scramble cobject labels without replacement
      randSet$cobject = sample(randSet$cobject,length(randSet$cobject))
      randSet$cDErc = sample(randSet$cDErc,length(randSet$cDErc))
      # test if target is related to random scrambled cobject
      onemodel = summary(lm(target ~ cobject*cDErc, randSet))
      coefonemodel = coef(onemodel)
      intT = as.numeric(coefonemodel[4,3])  # observed t-value
      randDCL = subset(randSet, HeadNoun=="DCL")
      onemodelDCL = summary(lm(target ~ cobject, randDCL))
      coefonemodelDCL = coef(onemodelDCL)
      dclstrT = as.numeric(coefonemodelDCL[2,3])  # observed t-value
      randDE = subset(randSet, HeadNoun=="DE")
      onemodelDE = summary(lm(target ~ cobject, randDE))
      coefonemodelDE = coef(onemodelDE)
      destrT = as.numeric(coefonemodelDE[2,3])  # observed t-value
      
      df = data.frame(t=intT,cluster=cl,time=b,sim=i,dclT=dclstrT,deT=destrT)
      exptests = rbind(exptests, df )
    }
  }
  save(exptests,file=filename)
  return(exptests)
}
#exptests = createPermDist("permDistMan5.RData") # since this takes a lot of time, we save the values in a file.
load("permDistMan5.RData") #this creates data frame exptests from file

# we sum over clusters so that longer clusters have stronger t-values
sumt.df =  aggregate(cbind(t,dclT,deT) ~cluster + sim, exptests, sum)
head(sumt.df)

# simulated sum cluster histogram
p = ggplot(sumt.df,aes(x = t))
p = p +geom_histogram(binwidth=0.5)
p+theme_bw()

```


```{r}
# this code extracts out the maximum sum t for each simulation at each age
if (length(unique(sumt.df$cluster)) > 1){ # only run if there is more than one cluster
maxclusterdist = data.frame()
  for (s in unique(sumt.df$sim)) {
    # get all results for one simulation in one HeadNounuage
    onesim = subset(sumt.df,sim == s)
    onesim$absT = abs(onesim$t)
    onesim$absdclT = abs(as.numeric(onesim$dclT))
    onesim$absdeT = abs(as.numeric(onesim$deT))
    # find max t-value
    maxrow = onesim[order(onesim$absT,decreasing = T),]
    maxclusterdist = rbind(maxclusterdist,maxrow[1,])
  }
}else{
  maxclusterdist = sumt.df
}
head(maxclusterdist)

# Shows the simulated distribution with maximum cluster t values
maxclusterdist2 = maxclusterdist[order(maxclusterdist$t),]
#end = data.frame(xint = maxclusterdist2[c(25,975,1025,1975),]$t)
p = ggplot(maxclusterdist,aes(x = t))
p = p +geom_histogram(binwidth=0.5)
#p = p +geom_vline(end,mapping=aes(xintercept=xint))
p+theme_bw()

```


```{r}

# maxclusterdist is sorted by HeadNounuage, 
# this identifies tvalues that are greater than dist t-values
for (cl in unique(sumcluster$cnum)){
  bins = unique(means.df[means.df$cnum == cl,]$time)

  # permtdist is the dist t-values, 
  # so p value is proportion of values greater than observed t-value.
  # absolute value gives two sided test
  intT = abs(sumcluster$intT[sumcluster$cnum==cl])
  intP = sum(abs(maxclusterdist$t) > intT, na.rm = TRUE)/length(maxclusterdist$t)
  if (intP < 0.05){
    print(paste("Cluster Interaction Term ",cl,"Obs.sum t",round(intT,3),"PropDist > observed p-value",intP))
  }
  
  destrT = abs(sumcluster$destrT[sumcluster$cnum==cl])
  deT = sum(abs(maxclusterdist$deT) > destrT, na.rm = TRUE)/length(maxclusterdist$deT)
  if (deT < 0.05){
    print(paste("Separate Test of deT only",cl,"Obs.sum t",round(destrT,3),"PropDist > observed p-value",deT))
  }
  
  dclstrT = abs(sumcluster$dclstrT[sumcluster$cnum==cl])
  dclT = sum(abs(maxclusterdist$dclT) > dclstrT, na.rm = TRUE)/length(maxclusterdist$dclT)
  if (dclT < 0.05){
    print(paste("Separate Test of dclT only",cl,"Obs.sum t",round(dclstrT,3),"PropDist > observed p-value",dclT))
  }

  means.df$permtestp[means.df$time %in% bins] = intP
}

# now we update our plot
p = ggplot(means.df , aes( x = time, y = target, linetype=SentenceType))
p = p + facet_wrap(~ HeadNoun, ncol=1)
# this pulls out the clusters which are significant by the permutation test
meansigStr = subset(means.df,permtestp < 0.025) 
# color them grey
if (length(meansigStr$time) > 0){
  p = p + geom_rect(data=meansigStr,aes(xmin=time-wsize-4, xmax=time+wsize+4, ymin = pliney+0.1, ymax= 1.0),colour=NA,fill="grey90",show.legend=FALSE)
}
# same as before
p = p + geom_line()
#p = p + scale_colour_brewer(palette="Set1")
#p = p + scale_fill_brewer(palette="Set2")
p = p + scale_linetype_discrete(name="RC Type")
p = p + theme_bw()   # change background to white
p = p + ylab("Target Proportion")
p = p + xlab("Time (msecs)")
#p = p + ylim(0,1)
p = p + geom_rect(aes(xmin=time-wsize, xmax=time+wsize, ymin = plineyInt, ymax= plineintP, fill=plinecolintP),colour=NA,show.legend=FALSE)
#p = p + geom_curve(data=meansigPost,aes(x=time+10, xend=time+winsize-10, y = 0.9, yend= 0.9),color="black",size=1, lineend = "square", curvature = -0.5, show.legend=FALSE)
p = p + geom_rect(data=onsetStim,aes(xmin=time,xmax = time2-33, ymin=ypos-0.13, ymax=ypos,linetype=SentenceType),fill=NA,colour="black", show.legend=FALSE)
p = p + geom_text(data=onsetStim,aes(x=(time+time2)/2, y=ypos-0.05, label=cat), hjust=0.7, size=3,show.legend=FALSE)
p = p +scale_colour_grey()
p = p +scale_fill_grey()
apaformat(p)
ggsave("permCan.png",width=8,height=6)
```





Here is some code that will report the results.

```{r}

modelComparison <- function(model,modellist=list(),verbose=0,filename="modellist.RData"){
  #  print(model)
  terms = attr(terms(model),"term.labels")
  modellist = append(modellist,model)
  #  print(terms)
  if (length(terms) > 0){
    newformula = paste(". ~ . - ",terms[length(terms)],"")
    print(paste("remove",newformula))
    model2 = update(model, as.formula(newformula))
    if (verbose > 0){
      print(summary(model2))
    }
    am1=anova(model2, model)
    print(am1)
    sig = ifelse(am1$`Pr(>Chisq)`[2]<0.05," *** ","")
    print(paste("########## Above comparison for ",terms[length(terms)],sig))
    
    terms = attr(terms(model),"term.labels")
    modellist = modelComparison(model2,modellist)
  }
  save(modellist, file= filename)
  return(modellist)
}

getModelNumHighestTerm <- function(varname,modellist) {
  for (i in 1:length(modellist)) {
    terms = attr(terms(modellist[[i]]), "term.labels")
    
    if (length(terms) > 0 & terms[length(terms)] == varname) {
      return(i)
    }
  }
  return(-1)
}

report <- function(varname, modellist){
  fullmodel=modellist[[1]]
  model.sum = summary(fullmodel)
  model.coef = coefficients(model.sum)
  outstr=""
  if (varname %in% rownames(model.coef)){
    oneline = model.coef[varname,]
    outstr = paste("$\\beta$=",round(oneline[[1]],3),", SE=",round(oneline[[2]],4),sep="")
  }
  
  tm = getModelNumHighestTerm(varname,modellist)
  model.anova = anova(modellist[[tm]],modellist[[tm+1]])
  chisqr = round(model.anova$Chisq[2],2)
  chisqrdf = model.anova$"Chi Df"[2]
  chisqrp = model.anova$"Pr(>Chisq)"[2]
  
  chisqrpf = format.pval(pv = chisqrp, digits = 2,eps=0.001,nsmall = 3)
  if (substr(chisqrpf,1,1)!='<'){
    chisqrpf = paste("=",chisqrpf,sep="")
  }
#  outstr = paste(c("beta","SE","z","p"),oneline,collapse=", ",sep="=")
  if (outstr != ""){
    outstr=paste(outstr,", ",sep="")
  }
  outstr = paste(outstr,"$\\chi^2$(",chisqrdf,")=",chisqr,", p",chisqrpf,sep="")
  return(outstr) 
}

modellist = modelComparison(mixmodel) # create anova table

# here are the start and finish bits
timedf = aggregate(time ~ cnum + HeadNoun,meansigStr,min)
colnames(timedf)<-c("cnum","HeadNoun","starttime")
timedf2 = aggregate(time ~ cnum + HeadNoun,meansigStr,max)
timedf$endtime = timedf2$time+33
print(timedf)
# significant regions in posthoc analysis
print(meansigPost)

print(summixed)
```


In this analysis, there was a main effect of window, `r report('cwin',modellist)`, and a marginal three-way interaction of window, RC type, and Head Noun `r report('cwin:cCL:cobject',modellist)`.  To explore this three-way interaction, posthoc comparisons were performed comparing subject and object RC types in each window in both studies (p-values were adjusted for the 24 multiple comparisons).  The only significant differences between subject and object was in the 2200-2400 window in the DE condition.  

```{r,fig.height=3}
accdf = read.csv("ManRC_accuracy_data_all_final.csv")

accdf$cCL = ifelse(accdf$structure == "DemCL",0.5,-0.5)
accdf$cobject = ifelse(accdf$extraction == "object",0.5,-0.5)
accdf$participant=factor(accdf$participant)
accdf$item = str_replace(accdf$item,"(S|O)","I")
accdf$item=factor(accdf$item)
xtabs( ~ structure + participant,accdf)
xtabs( ~ extraction + participant,accdf)
xtabs( ~ structure + item,accdf)
xtabs( ~ extraction + item,accdf)

acc.glm = glmer(Correct ~ cobject*cCL + (1 + extraction | participant) + (1 | item),accdf,family="binomial")
print(summary(acc.glm))

accdf$pred = remef(acc.glm, ran = "all")
head(accdf)
meandf = aggregate(Correct ~ extraction + structure, accdf, mean)
print(meandf)
# compute sd from pred without random effects
meandf$sd = aggregate(pred ~ extraction + structure, accdf,sd)$pred
print(meandf)
# se is computed from sd divided by number of participants
meandf$se = meandf$sd/sqrt( nlevels(accdf$participant) )
meandf$upper = meandf$Correct + meandf$se
meandf$lower = meandf$Correct - meandf$se
print(meandf)
meandf$extraction=factor(meandf$extraction,labels=c("Subject","Object"),levels=c("subject","object"))
meandf$structure=factor(meandf$structure,labels=c("DE","DCL"))

p = ggplot(meandf, aes(x=structure,y=Correct, fill=extraction,ymin = lower, ymax=upper))
p = p +geom_bar(stat="identity",position="dodge")
p = p +scale_fill_grey(name="RC Type")
p = p + xlab("Sentence Type")
p = p + geom_errorbar(width=0.25, position=position_dodge(.9) )
apaformat(p)
ggsave("accuracy.png",width=5,height=3)

```